---
title: "Untitled"
output: github_document
---

We will look at specific statistics and the correlations among them. 

### Aggregated data

Aggregated/summarized data is great for visualization. We can start at the "macroscopic" level of the league and teams. We use the `ggplot2` package for plotting because this tends to be the easiest way when dealing with grouping. The default theme is questionable, so add `theme_bw` to the `theme_set` function 

```{r}
library(dplyr)
library(ggplot2)
theme_set(theme_bw())

source('Finished_Functions.R')

url <- fg_url(Stats = 'bat', Type = 8, 
              Qual = '20', # arbitrary; a little under half of avg PA
              Month = 1000, 
              Max.results = 1000,
              Start.date = '2019-06-01',
              End.date = '2019-06-14')

df <- fg_table(url)
  
```

We start by looking at a histogram of the data to see the frequencies of batting averages, along with a formal test for normality.

```{r}
ggplot(df) + 
  geom_histogram(aes(AVG))

shapiro.test(df$AVG)

```

The data looks like it is normally-distributed across the league. This is backed by the Shapiro-Wilk test of normality (any p-value above 0.05 is typically considered normal). 

There's a pretty big drop in the number of players around a certain average around 0.350. We will consider this the "exceptional" range relative to the rest of the league.

```{r}
df.top <- df %>%
  filter(AVG > .350)

nrow(df.top) 
```

We can add text to the scatterplot to visualize how well the players are performing relative to each other. A lower number of plate appearances leaves less chances for a bad game or 2 (.000 batting avg.) to deflate your batting average. So we also want to consider the number of PA's a player had in this span of time. To do this on our graph, we add a transparency gradient.

```{r}
library(ggrepel)

ggplot(df.best) +
  geom_point(aes(x = iso, y = ISO)) +
  geom_text_repel(aes(x = SLG, y = AVG, 
                   label = Name, alpha = PA)) +
  theme(
    panel.grid.minor = element_blank() # for cleaner look
    )
```

Fun fact: we are looking at the ISO stat in the above graph. ISO stands for "isolated power" and is calculated as SLG - AVG.

### 2. Team performance
